\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{fancyhdr}

\setlength{\headheight}{15pt}
\pagestyle{fancy}
\fancyhf{}
\rhead{Computer Workshop Course}
\lhead{Final Assignment}
\rfoot{Page \thepage}

\title{Final project}
\author{abolfazl shahsavari}
\date{January 2024}

\begin{document}

\maketitle
\newpage
\tableofcontents
\newpage

\section{repository link}
\paragraph{\url{https://github.com/abolfazlshahsavary/FinalProject}}
\section{set up the repository}
\paragraph{To set up a repository, first of all,\\ we must have a GitHub account. After creating a GitHub account or \\logging into the account, we perform the following steps:}

\begin{itemize}
    \item Go to the repository section in your account
    \item Click on New Repository
    \item Select the repository owner and its name
    \item Enter the explation in the description field
    \item Choose whether your repository is public or private
    \item If you want to add a README to your repository and edit it later
    \item you can add licence to tell others the ablity of your code and what they can do with your code
    \item finaly click on creat repository 
\end{itemize}
\section{vim advance feature}
\begin{itemize}
    \item Vim Macros: Macros in Vim allow you to record a series of keystrokes and \\then play them back repeatedly. This feature can save you a lot of time when\\ performing repetitive tasks.  
    \item Vim Foldings: Foldings in Vim allow you to collapse and expand sections of code, making it easier to navigate and work with large files
    \item  Vim Registers: Registers in Vim allow you to store text snippets that you can easily paste into your document

\end{itemize}
\section{Memory profiling}
\paragraph{Memory leaks occur when a program allocates memory but fails to release it when it's no longer needed, leading to the waste of system resources and potentially causing performance issues or crashes. In other words, memory leaks result in the persistent use of memory that should have been freed up.

the most important reson for this problem is:\\

Forgetting to free dynamically allocated memory: In languages like C and C++, memory is allocated using functions like malloc or new, and it's the responsibility of the programmer to free the memory using functions like free\(\) or delete when it's no longer required. If the programmer forgets to free the memory, it will continue to occupy the allocated space, leading to a memory leak.\\ 
Valgrind is a powerful tool used for debugging and profiling Linux-based systems. Its primary purpose is to help developers identify and fix memory leaks, segmentation faults, and other memory-related issues in their programs.

Valgrind works by instrumenting the executable code of the program being debugged, which allows it to monitor the allocation and deallocation of memory, as well as other low-level system calls. It then generates detailed reports on the program's behavior, highlighting any potential issues and providing suggestions for improvement.

When memory leaks occur, Valgrind can help by identifying the specific lines of code where the memory is being allocated but not freed. This information can then be used to locate the source of the leak and develop a solution to prevent it from happening in the future.

Valgrind also provides detailed information on memory usage, including the amount of memory being allocated and deallocated, as well as any potential memory corruption issues that may arise due to incorrect pointer usage or buffer overflows/underflows in the program's codebase.. This information can help developers optimize their programs for memory usage and improve overall performance by reducing the amount of unnecessary memory allocation and deallocation that can lead to performance bottlenecks and slowdowns in large-scale applications}

\section{GNU/Linux Bash Scripting}
\subsection{fzf}
\paragraph{Fuzzy searching, also known as approximate searching, is a technique that allows users to find items that are similar to, but not exactly matching, their search query. This technique uses algorithms to calculate the similarity between a search query and the items being searched, based on factors such as edit distance, character similarity, and phonetic similarity. Fuzzy searching makes search processes more flexible and forgiving, as users no longer have to worry about exact spelling or formatting requirements, making it particularly useful in applications such as search engines, spell checkers, and text editors where typos or misspellings are common.\\}
\paragraph{The command `ls | fzf is a combination of two Linux commands that allows you to use fuzzy searching to filter the output of the ls (list) command. 

First, ls lists the contents of the current directory. Then, \| \(pipe\) redirects the output of ls to fzf, a fuzzy finder utility. fzf displays a list of the files and directories found by ls, and allows you to filter and select items using fuzzy searching. You can use the arrow keys to navigate the list, and press Enter to select an item. This can be a faster and more efficient way to find specific files or directories, especially if you have a large number of items in your directory.}


\subsection{Using fzf to find your favorite PDF}
\paragraph{}
\subsection{Opening the file using Zathura}


\end{document}